Technique for \earlywarning\ detection of compact binary coalescence and its implication for multi-messenger astronomy

### 2011-06-03 method.tex
Some tweaks to symbol table
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@851 ccdd05d5-56c1-461a-bf98-85f6876523b4

We now examine the computational cost scaling of the approximate implementation
of \eqref{eq:SNRTD} as \eqref{eq:decomp}.  An actual implementation of this
decomposition in a working analysis pipeline is discussed in the next section
along with measured computational requirements.  For convenience, table
\ref{tab:recap} is a recap of the meaning of various symbols used in this
calculation.
%
% symbols used in FLOPs calculations table
%
\begin{table}
\begin{tabular}{rl}
\bf{Symbol}	& \bf{Definition} \\
\hline
\tmpsamps	& The number of sample points in template $x_i$ \\
\numtmps	& The number of templates in the set $\{x_i\}$ \\
\numslices	& The number of time slices \\
\numsvdtmps	& The number of orthogonal filters in time slice $k$ \\
\slicessamps	& The number of samples in time slice $k$ \\
\fmax		& The maximum frequency of a filter \\
$f^s$		& The sample frequency of the $k^{\mathrm{th}}$ filter \\
\resampsamps	& The number of sample points in the resample filter
\end{tabular}
\caption{\label{tab:recap} Notation used to describe filtering.  This table
provides a quick reference for symbols used.}
\end{table}

>>>>

We now examine the computational cost scaling of the approximate implementation
of \eqref{eq:SNRTD} as \eqref{eq:decomp}.  An actual implementation of this
decomposition in a working analysis pipeline is discussed in the next section
along with measured computational requirements.  For convenience, table
\ref{tab:recap} is a recap of the meaning of various symbols used in this
calculation.
%
% symbols used in FLOPs calculations table
%
\begin{table}
\begin{tabular}{rl}
\bf{Symbol}	& \bf{Definition} \\
\hline
\tmpsamps	& The number of sample points per template \\
\numtmps		& The number of templates \\
\numslices	& The number of time slices \\
\numsvdtmps	& The number of orthogonal templates in time slice $s$ \\
\slicessamps	& The number of samples in time slice $s$ \\
$f^s$		& The sample rate in time slice $s$ \\
\resampsamps	& The number of coefficients in the decimation and interpolation filters
\end{tabular}
\caption{\label{tab:recap} Notation used to describe filters.  This table
provides a quick reference for symbols used.}
\end{table}
